Scalable Clustering of Genotype Information using MapReduce

### 2014-05-01 doc/publications/incob2014/paper.tex
initial setup for a methodology paper in BMC Genomics

%\documentclass[twocolumn]{bmcart}% uncomment this for twocolumn layout and comment line below
\documentclass{bmcart}

@@

\begin{fmbox}
\dochead{Research}

@@

\title{A sample article title}

@@

\author[
   addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
   corref={aff1},                       % id of corresponding address, if any
   noteref={n1},                        % id's of article notes, if any
   email={jane.e.doe@cambridge.co.uk}   % email address
]{\inits{JE}\fnm{Jane E} \snm{Doe}}
\author[
   addressref={aff1,aff2},
   email={john.RS.Smith@cambridge.co.uk}
]{\inits{JRS}\fnm{John RS} \snm{Smith}}

@@

\address[id=aff1]{%                           % unique id
  \orgname{Department of Zoology, Cambridge}, % university, etc
  \street{Waterloo Road},                     %
  %\postcode{}                                % post or zip code
  \city{London},                              % city
  \cny{UK}                                    % country
}
\address[id=aff2]{%
  \orgname{Marine Ecology Department, Institute of Marine Sciences Kiel},
  \street{D\"{u}sternbrooker Weg 20},
  \postcode{24105}
  \city{Kiel},
  \cny{Germany}
}

@@

\begin{artnotes}
%\note{Sample of title note}     % note to the article
\note[id=n1]{Equal contributor} % note, connected to author
\end{artnotes}

\end{fmbox}% comment this for two column layout

@@

\begin{abstract} % abstract
\parttitle{First part title} %if any
Text for this section.

\parttitle{Second part title} %if any
Text for this section.
\end{abstract}

@@

\begin{keyword}
\kwd{sample}
\kwd{article}
\kwd{author}
\end{keyword}

@@

\end{abstractbox}
%
%\end{fmbox}% uncomment this for twcolumn layout

@@

%%%%%%%%%%%%%%%%
%% Background %%
%%
\section*{Content}
Text and results for this section, as per the individual journal's instructions for authors. %\cite{koon,oreg,khar,zvai,xjon,schn,pond,smith,marg,hunn,advi,koha,mouse}

\section*{Background}
Text for this section.

\section*{Runtime}
Text for this section.

\section*{Accuracy}
Text for this section.

\section*{Real World Example}
Text for this section.

K-means clustering 
We Cluster samples from a VCF file containing the variants from chromosome one. The content of the VCF file represents
Mahout provides libraries for clustering data, 'sequences', although the data must first be converted from the VCF format to
sequence files. The sequence files should consist of key-value pairs, where
Using a custom Java program, we transpose the

\subsection*{Sub-heading for section}
Text for this sub-heading \ldots
\subsubsection*{Sub-sub heading for section}
Text for this sub-sub-heading \ldots
\paragraph*{Sub-sub-sub heading for section}
Text for this sub-sub-sub-headi	ng \ldots
In this section we examine the growth rate of the mean of $Z_0$, $Z_1$ and $Z_2$. In
addition, we examine a common modeling assumption and note the
importance of considering the tails of the extinction time $T_x$ in
studies of escape dynamics.
We will first consider the expected resistant population at $vT_x$ for
some $v>0$, (and temporarily assume $\alpha=0$)
%

%
If we assume that sensitive cells follow a deterministic decay
$Z_0(t)=xe^{\lambda_0 t}$ and approximate their extinction time as
$T_x\approx-\frac{1}{\lambda_0}\log x$, then we can heuristically
estimate the expected value as
%

%
Thus we observe that this expected value is finite for all $v>0$ (also see \cite{koon,khar,zvai,xjon,marg}).

@@

@@

% if your bibliography is in bibtex format, use those commands:
\bibliographystyle{bmc-mathphys} % Style BST file
\bibliography{bmc_article}      % Bibliography file (usually '*.bib' )

>>>>

\documentclass[twocolumn]{bmcart}% uncomment this for twocolumn layout and comment line below
%\documentclass{bmcart}

@@

\begin{fmbox}
\dochead{Methodology}

@@

\title{Scalable Clustering of Genotype Information using MapReduce}

@@

\author[
   addressref={aff1,aff2},                   % id's of addresses, e.g. {aff1,aff2}
%   noteref={n1},                        % id's of article notes, if any
   email={Aidan.O'Brien@csiro.au}   % email address
]{\inits{AR}\fnm{Aidan R} \snm{O'Brien}}
\author[
   addressref={aff2},
   email={f.buske@garvan.org.au}
]{\inits{FA}\fnm{Fabian A} \snm{Buske}}
\author[
   addressref={aff1},
   corref={aff1},                       % id of corresponding address, if any
   email={Denis.Bauer@CSIRO.au}
]{\inits{DC}\fnm{Denis C} \snm{Bauer}}

@@

\address[id=aff1]{%                           % unique id
  \orgname{Division of Computational Informatics, CSIRO}, % university, etc
  \street{11 Julius Av},                     %
  \postcode{2113}                                % post or zip code
  \city{Sydney},                              % city
  \cny{Australia}                                    % country
}
\address[id=aff2]{%
  \orgname{School of Biomedical Sciences and Pharmacy, Faculty of Health},
%  \street{},
  \postcode{2308}
  \city{Newcastle},
  \cny{Australia}
}
\address[id=aff3]{%
  \orgname{Cancer Epigenetics Program, Cancer Research Division, Kinghorn Cancer Centre, Garvan Institute of Medical Research},
  \street{384 Victoria St},
  \postcode{2010}
  \city{Sydney},
  \cny{Australia}
}

@@

%\begin{artnotes}
%\note{Sample of title note}     % note to the article
%\note[id=n1]{Equal contributor} % note, connected to author
%\end{artnotes}

%\end{fmbox}% comment this for two column layout

@@

\begin{abstract} % abstract
\parttitle{Background}
\parttitle{Results}
\parttitle{Conclusions}
\end{abstract}

@@

\begin{keyword}
\kwd{Hadoop}
\kwd{Mahout}
\kwd{Genotype}
\kwd{Clustering}
\kwd{MapReduce}
\end{keyword}

@@

\end{abstractbox}
%
\end{fmbox}% uncomment this for twcolumn layout

@@

%%%%%%%%%%%%%%%%
%% Background %%
%%
\section*{Background}
Text for this section.

\section*{Results and discussion}
\subsection*{Runtime}
Text for this section.

\subsection*{Accuracy}
Text for this section.

\subsection*{Real World Example}
Text for this section.

\section*{Conclusion}

\section*{Methods}
\subsection*{K-means clustering}
We Cluster samples from a VCF file containing the variants from chromosome one. The content of the VCF file represents
Mahout provides libraries for clustering data, 'sequences', although the data must first be converted from the VCF format to
sequence files. The sequence files should consist of key-value pairs, where
Using a custom Java program, we transpose the

@@

\section*{Availability of supporting data}
\section*{List of abbreviations}

@@

% if your bibliography is in bibtex format, use those commands:
\bibliographystyle{bmc-mathphys} % Style BST file
\bibliography{genotypeClustering}      % Bibliography file (usually '*.bib' )
